Implicit yaddayadda

### 2011-10-28 papers/PLDI2012/implicitization.tex
hop
je remets phd de nicolas

\section{Introduction}
Static analysis by abstract interpretation is a fully automatic program analysis method. When applied to imperative programs, it computes an inductive invariant mapping each program location (or a subset thereof) to a set of states represented symbolically~\cite{CousotCousot_JLC92}.
For instance, if we are only interested in scalar numerical program variables, such a set may be a convex polyhedron (the set of solutions of a system of linear inequalities)~\cite{CousotHalbwachs78,PPL,BagnaraHZ08SCP}.

@@

All these methods improve the precision of the analysis by keeping the same abstract domain (say, convex polyhedra) but changing the operations applied and their ordering. An alternative is to change the abstract domain, for instance by moving from intervals to octagons or convex polyhedra \cite{DBLP:journals/lisp/Mine06}, or the widening operator: for instance one may replace the classical widening on convex polyhedra \cite{CousotHalbwachs78} by an improved version \cite{BagnaraHRZ05SCP}, or use widening ``up to'', that is, use linear inequalities syntactically present in the program source code as possible widening steps~\cite{Polka:FMSD:97}.

@@

>>>>

\section{Introduction}
Static analysis by abstract interpretation is a fully automatic program analysis method. When applied to imperative programs, it computes an inductive invariant mapping each program location (or a subset thereof) to a set of states represented symbolically~\cite{CousotCousot_JLC92}.
For instance, if we are only interested in scalar numerical program variables, such a set may be a convex polyhedron (the set of solutions of a system of linear inequalities)~\cite{CousotHalbwachs78,Halbwachs_PhD,PPL,BagnaraHZ08SCP}.

@@

All these methods improve the precision of the analysis by keeping the same abstract domain (say, convex polyhedra) but changing the operations applied and their ordering. An alternative is to change the abstract domain, for instance by moving from intervals to octagons or convex polyhedra \cite{DBLP:journals/lisp/Mine06}, or the widening operator: for instance one may replace the classical widening on convex polyhedra \cite{CousotHalbwachs78,Halbwachs_PhD} by an improved version \cite{BagnaraHRZ05SCP}, or use widening ``up to'', that is, use linear inequalities syntactically present in the program source code as possible widening steps~\cite{Polka:FMSD:97}.

@@

\DM{Garde-t-on la these en francais de Nicolas?}
